Fast Neural Machine Translation Implementation

### 2018-05-18 wnmt.2018/wnmt.tex
bah

  \author{Hieu Hoang$^{\dagger}$ \, Tomasz Dwojak$^{*}$ \, Rihards Krislauks$^{\ddagger}$ \\ {\bf Daniel Torregrosa$^{\mathparagraph}$ \, Kenneth Heafield$^{\dagger}$ } \\[2mm]
  $^{\dagger}$University of Edinburgh \, $^{*}$Adam Mickiewicz University in Pozna\'{n} \\ $^{\ddagger}$Tilde \,  $^{\mathparagraph}$Universitat d'Alacant }

@@

We take an opposing approach by eschewing model selection in favour of efficient implementation. We use and enhanced a custom inference engine, Amun~\citep{junczys2016neural}, which we developed on the premise that fast deep-learning inference is an issue that deserves dedicated tools that are not compromised by competing objectives such as training or support for multiple models. As well as delivering on the practical goal of fast inference, it can serve as a test-bed for novel ideas on neural network inference, and is useful as a mean to explore the upper bound of the possible speed for a particular model and hardware. That is, Amun is an inference-only engine that supports a limited number of NMT models that put fast inference on modern GPU above all other considerations. %The consequence of this focused approach can be seen in the results of the shared task ???.

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Batching}{encoded sentences $i$, beam size $s$}

\State Create batch $b$ from $i$, $s$

\While{hypo $h \neq \textless/s \textgreater, \forall h \in b $ } 
  \State $b$ = DecodeAndBeamSearch($b$)
\EndWhile

@@

\While{$b \neq \emptyset$} 
  \State $b' \gets$ DecodeAndBeamSearch($b$)
  \State $b \gets \emptyset$

  \ForAll{hypo $h \in b'$}
    \If{$h \neq \textless/s \textgreater$  }
      \State Add $h$ to $b$
    \EndIf
  \EndFor
\EndWhile

>>>>

  \author{Hieu Hoang$^{\dagger}$ \, Tomasz Dwojak$^{*}$ \, Rihards Krislauks$^{\ddagger}$ \\ {\bf Daniel Torregrosa$^{\mathparagraph}$ \, Kenneth Heafield$^{\dagger}$ } \\[2mm]
  $^{\dagger}$University of Edinburgh \, $^{*}$Adam Mickiewicz University \\ $^{\ddagger}$Tilde \,  $^{\mathparagraph}$Universitat d'Alacant }

@@

We take an opposing approach by eschewing model selection and parameter tuning in favour of efficient implementation. We use and enhanced a custom inference engine, Amun~\citep{junczys2016neural}, which we developed on the premise that fast deep-learning inference is an issue that deserves dedicated tools that are not compromised by competing objectives such as training or support for multiple models. As well as delivering on the practical goal of fast inference, it can serve as a test-bed for novel ideas on neural network inference, and is useful as a mean to explore the upper bound of the possible speed for a particular model and hardware. That is, Amun is an inference-only engine that supports a limited number of NMT models that put fast inference on modern GPU above all other considerations. %The consequence of this focused approach can be seen in the results of the shared task ???.

@@

\While{hypo $h \neq EOS, \forall h \in b $ } 
  \State Decode($b$)
\EndWhile

@@

\While{$b \neq \emptyset$} 
  \State Decode($b$)

  \ForAll{hypo $h \in b$}
    \If{$h = EOS$  }
      \State Remove $h$ from $b$
    \EndIf
  \EndFor
\EndWhile
